### 2016-06-29 GPCE2016/sections/Introduction.tex
Introduction and Abstract

Another advantage of IB is support for
multiple inheritance. The literature is rich on how
easy it is to combine multiple sources of pure behaviour,
using mechanisms such as traits~\cite{scharli03traits}. In Java
multiple \emph{interface} inheritance has been supported since
inception, and Java 8 default methods~\cite{goetz12fdefenders} bring some of the
advantages of traits to Java. The literature~\cite{Sak89dis,bracha90mixin,malayeri2009cz}
is also rich on how hard it is to combine multiple sources
of behaviour \textbf{and} state with multiple \emph{implementation}
inheritance of classes. In IB there is only multiple
interface inheritance, yet programmers can still use state via 
abstract state operations. IB enables powerful
idioms using multiple inheritance and state.

@@

While the Java embedding has obvious advantages from the practical
point-of-view, it also imposes some limitations that a new IB language
would not have. Supporting proper encapsulation is
difficult in Java due to limitations of Java interfaces. In particular
in Java interfaces the visibility of all methods is public. Thus
modelling private state is difficult in current Java 8. However,
 using existing design patterns~\cite{BettiniDSS13} we can emulate hiding
methods from interfaces. Furthermore Java 9 will allow private methods
on interfaces~\cite{srikanth16private}, greatly improving the support for
encapsulation.

@@

\item {\bf Classless Java:} a practical realization of IB in
  Java. Classless Java is implemented using annotation processing,
  allowing most tools to work transparently with our approach. 
  Existing Java projects can use our approach and still be
  backward compatible with their clients, in a way that is specified
  by our safety properties. A formal semantics is available in an extended report~\footnote{url}.

>>>>

Another advantage of IB is support for
multiple inheritance. The literature shows how
easy it is to combine multiple sources of pure behaviour,
using traits~\cite{scharli03traits}. In Java
multiple \emph{interface} inheritance has been supported since
inception, and Java 8 default methods~\cite{goetz12fdefenders} bring some of the
advantages of traits to Java. The literature~\cite{Sak89dis,bracha90mixin,malayeri2009cz}
is also rich on how hard it is to combine multiple sources
of behaviour \textbf{and} state with multiple \emph{implementation}
inheritance of classes. In IB there is only multiple
interface inheritance, yet programmers can still use state via 
abstract state operations. IB enables powerful
idioms using multiple inheritance and state.

@@

While the Java embedding has obvious advantages from the practical
point-of-view, it also imposes some limitations that a new IB language
would not have. Supporting proper encapsulation is
difficult in Java due to limitations of Java interfaces. In particular
in Java interfaces the visibility of all methods is public. Thus
modelling private state is difficult in current Java 8. However,
 using existing design patterns~\cite{BettiniDSS13} we can emulate hiding
methods from interfaces. Furthermore Java 9 will allow private methods
on interfaces~\cite{srikanth16private}.

@@

\item {\bf Classless Java:} a practical realization of IB in
  Java. Classless Java is implemented using annotation processing,
  allowing most tools to work transparently with our approach. 
  Existing Java projects can use our approach and still be
  backward compatible with their clients, in a way that is specified
  by our safety properties. A formal translation to Java is available in an extended report\footnote{url}.
